SAT Solving for Vesicle Traffic Systems in Cells

### 2017-06-13 paper/experiments.tex
table added

We have implemented the encoding of the constraints
in the python interface of $\zthree$

>>>>

We have implemented the encoding of the constraints
in the python interface of $\zthree$.
%
Our implementation supports several versions of the
models of vesicle traffic systems.
\todo{describe the variations}
\begin{itemize}
\item 
\end{itemize}

We have applied the tool for the above variations
for searching the vesicle traffic systems that satisfies
their corresponding properties.
%
\input{tbl-qf-graph}
In table~\ref{tbl:qf-results}

\todo{Make table for all sizes and variants of the tool}
